Is essentiality of genes conserved in Enterobacteriaceae?

### 2018-08-03 documents/manuscript.tex
Compared essentiality prediction of genes using different bias corrections

% line numbers
\usepackage[right]{lineno}
\linenumbers

@@

Ten genes are only ancestrally essential in \textit{Salmonella} which are shown in Supplementary Figure 12. Among these are \textit{fepC}, \textit{fepD}, and \textit{fepG}. \textit{FepB} is also essnetial in 3 out of 6 \textit{Salmonella} genomes in this study, but is not defined as ancestrally essential using Fitch's algorithm. These four genes have been previously shown to be essential in \textit{S.} Typhi and non-essential in \textit{S.} Typhimurium SL1344 \cite{barquist_comparison_2013}. Our analysis shows that they are also essential in \textit{S.} Enteritidis, \textit{S.} Typhimurium D23580, and \textit{S.} Typhimurium A130. This shows the importance of the import of Ferric iron in these genomes. \textit{FtsE} and \textit{ftsX} are other accessory essential genes in \textit{Salmonella}. These genes are ABC transporters that facilitate cell division.%These genes are mostly ABC transporters. As ABC transporters are a large family of genes, some genes in this family might be able to perform the same functions in other genera.

Seven genes are exclusively essential in \textit{Escherichia}. One of these genes is \textit{hipB} which is an antitoxin and is essential in \textit{Escherichia} whenever the toxin (hipA) is present. Another gene in this group is \textit{rpsI} which is 30S ribosomal protein S9. Although this gene has appeared as essential in our study and Keio collection \cite{baba_construction_2006}, it is shown that \textit{E. coli} is viable without this gene despite its slow growth \cite{bubunenko_essentiality_2007, shoji_systematic_2011}. Two other genes in this group are \textit{PhoU} which is a phosphate specific transport system accessory protein whose mutation causes the accumulation of inorganic phosphate in \textit{E. coli} \cite{morohoshi_accumulation_2002} and \textit{crr} which is a component of glucose-specific phosphotransferase enzyme.
%which are involved in different processes and complexes, such as ribosome, quorum sensing, and glycolysis.

>>>>

% line numbers
%\usepackage[right]{lineno}
%\linenumbers

@@

Ten genes are only ancestrally essential in \textit{Salmonella} which are shown in Supplementary Figure 12. Among these are \textit{fepC}, \textit{fepD}, and \textit{fepG}. \textit{FepB} is also essential in 3 out of 6 \textit{Salmonella} genomes in this study, but is not defined as ancestrally essential using Fitch's algorithm. These four genes have been previously shown to be essential in \textit{S.} Typhi and non-essential in \textit{S.} Typhimurium SL1344 \cite{barquist_comparison_2013}. Our analysis shows that they are also essential in \textit{S.} Enteritidis, \textit{S.} Typhimurium D23580, and \textit{S.} Typhimurium A130. This shows the importance of the import of Ferric iron in these genomes. \textit{FtsE} and \textit{ftsX} are other accessory essential genes in \textit{Salmonella}. These genes are ABC transporters that facilitate cell division.%These genes are mostly ABC transporters. As ABC transporters are a large family of genes, some genes in this family might be able to perform the same functions in other genera.

Seven genes are exclusively essential in \textit{Escherichia}. One of these genes is \textit{hipB} which is an antitoxin and is essential in \textit{Escherichia} whenever the toxin (\textit{hipA}) is present. Another gene in this group is \textit{rpsI} which is 30S ribosomal protein S9. Although this gene has appeared as essential in our study and Keio collection \cite{baba_construction_2006}, it is shown that \textit{E. coli} is viable without this gene despite its slow growth \cite{bubunenko_essentiality_2007, shoji_systematic_2011}. Two other genes in this group are \textit{PhoU} which is a phosphate specific transport system accessory protein whose mutation causes the accumulation of inorganic phosphate in \textit{E. coli} \cite{morohoshi_accumulation_2002} and \textit{crr} which is a component of glucose-specific phosphotransferase enzyme.
%which are involved in different processes and complexes, such as ribosome, quorum sensing, and glycolysis.
